Modelling BCG vaccination in the UK

### 2019-12-16 rmds/00-contribution.Rmd
updated html thesis stuff
review abstract + contribution
acronyms updated
updated getTBinR title
added Sutherland changes

Abbott S. *getTBinR: an R package for accessing and summarising the World Health Organisation Tuberculosis data*,
Journal of Open Source Software, 2019, 4(34), 1260., doi: https://doi.org/10.21105/joss.01260 \par

@@

Abbott S, Christensen H, Brooks-Pollock E. *Reassessing the evidence for universal school-age Bacillus Calmette Guerin (BCG) vaccination in England and Wales*, doi: https://doi.org/10.1101/567511 \par

@@

Abbott, S., Christensen, H., Lalor, M. K., Zenner, D., Campbell, C., Ramsay, M. E., & Brooks-Pollock, E. (2019). *Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: Observational study using the Enhanced Tuberculosis Surveillance system*. Vaccine, 1–6. doi: http://doi.org/10.1016/j.vaccine.2019.06.056 (preprint: https://doi.org/10.1101/366476) \par

@@

Abbott S, Christensen H, Welton NJ, Brooks-Pollock E. *Estimating the effect of the 2005 change in BCG policy in England: A retrospective cohort study*, doi: https://doi.org/10.1101/567511 \par

@@

@@

Date: *placeholder*

>>>>

Abbott S. *getTBinR: an R package for accessing and summarising the World Health Organisation Tuberculosis data*,
Journal of Open Source Software, 2019, 4(34), 1260. doi: https://doi.org/10.21105/joss.01260 \par

@@

Abbott S., Christensen H., Brooks-Pollock E. *Reassessing the evidence for universal school-age Bacillus Calmette Guerin (BCG) vaccination in England and Wales*. doi: https://doi.org/10.1101/567511 \par

@@

Abbott S., Christensen H., Lalor M. K., Zenner D., Campbell C., Ramsay M. E., & Brooks-Pollock, E. (2019). *Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: Observational study using the Enhanced Tuberculosis Surveillance system*. Vaccine, 1–6. doi: http://doi.org/10.1016/j.vaccine.2019.06.056 (preprint: https://doi.org/10.1101/366476) \par

@@

Abbott S., Christensen H., Welton N.J., Brooks-Pollock E. (2019) *Estimating the effect of the 2005 change in BCG policy in England: a retrospective cohort study, 2000 to 2015*. Eurosurveillance, 49(24). doi: https://doi.org/10.2807/1560-7917.ES.2019.24.49.1900220 \par

@@

\vspace{10mm}

@@

\vspace{10mm}

Date:

### 2019-12-16 rmds/01-introduction.Rmd
added Sutherland changes

@@

* Abbott S., Christensen H., Welton N.J., Brooks-Pollock E.. *Estimating the effect of the 2005 change in BCG policy in England: A retrospective cohort study*, doi: https://doi.org/10.1101/567511

>>>>

* Abbott S., Christensen H., Welton N.J., Brooks-Pollock E. (2019) *Estimating the effect of the 2005 change in BCG policy in England: a retrospective cohort study, 2000 to 2015*. Eurosurveillance, 49(24). doi: https://doi.org/10.2807/1560-7917.ES.2019.24.49.1900220 (preprint: https://doi.org/10.1101/567511)

@@

### 2019-12-16 rmds/05-evidence-policy-change.Rmd
added Sutherland changes

```{r plot-annual-change, fig.scap = "Annual percentage change in ethnic White UK born incidence rates for those aged 15-19, 20-24, and 25-29 years old under different scenarios.", fig.cap = "Annual percentage change in ethnic White UK born incidence rates for those aged 15-19, 20-24, and 25-29 years old under different scenarios. For the notification and incidence rate scenarios each line represents the median of 10,000 parameter samples.", out.extra = ""}
knitr::include_graphics("chapters/evidence-policy-change/fig-1.tiff")
```

@@

```{r graph-avg-add-not, fig.scap = "Annual additional (stratified into primary and secondary) notifications in 15-29 year olds from stopping the BCG schools scheme in 2006, and 2011 until 2028.", fig.cap = "Annual additional (stratified into primary and secondary) notifications in 15-29 year olds from stopping the BCG schools scheme in 2006, and 2011 until 2028. The years presented were dictated by the 5-year timestep of the model. The percentage annual decrease scenarios considered were based on those considered by the JCVI BCG subgroup. Data based scenarios and the JCVI 0% decrease scenario were not presented here as the updated transmission model could not support these scenarios. Each boxplot summarises the output of 10,000 model simulations for each scenario. Secondary notifications are reported assuming they occurred in the same year as the primary notifications that caused them.", out.extra = ""}
knitr::include_graphics("chapters/evidence-policy-change/fig-3.tiff")
```

>>>>

```{r plot-annual-change, fig.scap = "Annual percentage change in ethnic White UK born incidence rates for those aged 15-19, 20-24, and 25-29 years old under different scenarios.", fig.cap = "Annual percentage change in ethnic White UK born incidence rates for those aged 15-19, 20-24, and 25-29 years old under different scenarios. For the notification and incidence rate scenarios each line represents the median of 10,000 parameter samples.", out.extra = ""}
knitr::include_graphics("chapters/evidence-policy-change/fig-1.png")
```

@@

```{r graph-avg-add-not, fig.scap = "Annual additional (stratified into primary and secondary) notifications in 15-29 year olds from stopping the BCG schools scheme in 2006, and 2011 until 2028.", fig.cap = "Annual additional (stratified into primary and secondary) notifications in 15-29 year olds from stopping the BCG schools scheme in 2006, and 2011 until 2028. The years presented were dictated by the 5-year timestep of the model. The percentage annual decrease scenarios considered were based on those considered by the JCVI BCG subgroup. Data based scenarios and the JCVI 0% decrease scenario were not presented here as the updated transmission model could not support these scenarios. Each boxplot summarises the output of 10,000 model simulations for each scenario. Secondary notifications are reported assuming they occurred in the same year as the primary notifications that caused them.", out.extra = ""}
knitr::include_graphics("chapters/evidence-policy-change/fig-3.png")
```

### 2019-12-16 rmds/07-direct-effect-bcg-change.Rmd
added Sutherland changes

I combined notification data from the Enhanced TB Surveillance (ETS) system, with demographic data from the Labour Force Survey (LFS) to construct retrospective cohorts of individuals in England relevant to both the universal, and targeted vaccination programmes between Jan 1, 2000 and Dec 31, 2010. For each cohort, I estimated incidence rates over a 5 year follow-up period and used Poisson and negative binomial regression models in order to estimate the impact of the change in policy on TB. This work was adapted from a preprint^[Preprint: https://doi.org/10.1101/567511] supervised by Hannah Christensen and Ellen Brooks-Pollock. Nicky Welton provided guidance on the statistical methods used.

>>>>

I combined notification data from the Enhanced TB Surveillance (ETS) system, with demographic data from the Labour Force Survey (LFS) to construct retrospective cohorts of individuals in England relevant to both the universal, and targeted vaccination programmes between Jan 1, 2000 and Dec 31, 2010. For each cohort, I estimated incidence rates over a 5 year follow-up period and used Poisson and negative binomial regression models in order to estimate the impact of the change in policy on TB. This work was adapted from a paper^[Paper: https://doi.org/10.2807/1560-7917.ES.2019.24.49.1900220 Preprint: https://doi.org/10.1101/567511] supervised by Hannah Christensen and Ellen Brooks-Pollock.[@Abbott567511] Nicky Welton provided guidance on the statistical methods used.
